Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-29 colt-21/cvx-flats.tex
Refining Cor 15 sketch

        \jessiet{Adding an attempt at first paragraph of sketch below, but also my brain isn't functioning.}
    If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
    Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ contained in $\gamma_r$.
    In particular, if $p \in \relint{\simplex}$, we can verify $\spn(F) \subseteq \Sc_{\gamma_r}(p) + \{p\}$.
    The feasible subspace (shifted by $p$) spans\jessiet{not the word I want...} $\relint{\simplex}$, and we can observe that the shifted feasible subspace is full dimensional relative to $\affhull(\simplex)$.
    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq n-1-\dim(\Sc_{\gamma_r(p)})$.

>>>>

        \jessiet{Adding an attempt at first paragraph of sketch below, but also my brain isn't functioning.}
    If $\conscvx(\gamma) \leq d$, then there is a $L \in \Lcvx_d$ so that $L$ is consistent with respect to $\gamma$, and in turn, indirectly elicits $\gamma$.
    Lemma~\ref{lem:convex-flats-inf-dim} says that there is some $d$-flat $F = \zeros{V}$ such that $p \in F \subseteq \gamma_r$.
    In particular, if $p \in \relint{\simplex}$, this object has the same dimension as $\Sc_{\gamma_r}(p)$, relative to $\affhull(\simplex)$, whose dimension is $|\Y| - 1 = \|p\|_0 - 1$.
    We then use the rank-nullity theorem with a bound on $\rank(V) \leq d$ to obtain the bound $d \geq \|p\|_0-1-\dim(\Sc_{\gamma_r}(p))$.
